---
title: "Plottly over baseball data set"
author: "Santiago Humberto Londoño Restrepo"
date: "10 de julio de 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!


## Solution

The following graph shows a scatter plot for Baseball from the 1986 and 1987 seasons data. On the axis and the variable is Salary (1987 annual salary on opening day in thousands of dollars), on the x-axis the variable is CHmRun (Number of home runs during his career). We add other variables in the same graph, through the color we represent the variable CRBI (Number of runs batted in during his career) and the two grids express the variable Division (A factor with levels E and W indicating player's division at the end Of 1986).

It is observed that the salary of the players increases to more number of home runs and batted races during their races. Taking into account the variable Division, it is observed that the positive relationship between salary with the variables CHmRun and CRBI is stronger in Division E than in Division W.

Unfortunately I can not distinguish the name of the axes, I tried to solve this problem by modifying the option fig.align = 'center' of the code chunks but nothing happens. If you have any idea, let me know.


```{r, message=FALSE, warning=FALSE,fig.align='center',fig.height=3, fig.width=5,echo=FALSE}

#Package with data
library(ISLR)

#My favorite plot system
library(ggplot2)

#Hitters is a Baseball Data
data("Hitters")

#Load plotly library
library(plotly)
plot1 <- ggplot(Hitters, aes(y=Salary, x=CHmRun, col=CRBI)) + 
        geom_point(lwd=2, alpha=0.8) + facet_grid(.~ Division)+
        xlab("CHmRun") +
        ylab("Salary")

ggplotly(plot1)

```


The following code shows how the previous graph is constructed.

```{r, message=FALSE, warning=FALSE,fig.align='center',fig.height=3, fig.width=5,eval=FALSE, echo=TRUE}
#Package with data
library(ISLR)

#My favorite plot system
library(ggplot2)

#Hitters is a Baseball Data
data("Hitters")

#Load plotly library
library(plotly)
plot1 <- ggplot(Hitters, aes(y=Salary, x=CHmRun, col=CRBI)) + 
        geom_point(lwd=2, alpha=0.8) + facet_grid(.~ Division)+
        xlab("CHmRun") +
        ylab("Salary")

ggplotly(plot1)
```
